04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
updated pca plots

```{r pca}
hypPCA <- returnPCAs2(dds.hypothalamus)
plotPC12(hypPCA, "female and male hypothalamus")

pitPCA <- returnPCAs2(dds.pituitary)
plotPC12(pitPCA, "female and male pituitary")

gonPCA <- returnPCAs2(dds.gonad)
plotPC12(gonPCA, "female and male gonad")
```

>>>>

```{r pca}
theme_set(theme_classic())

hypPCA <- returnPCAs2(dds.hypothalamus)
plotPC12(hypPCA, "Hypothalamus")

pitPCA <- returnPCAs2(dds.pituitary)
plotPC12(pitPCA, "Pituitary")

gonPCA <- returnPCAs2(dds.gonad)
plotPC12(gonPCA, "Gonad")
```
